---
title: "Flow Cytometry Data Analysis"
author: "Francesca Dellacqua"
date: "4/04/2022"
output: html_document
---

```{r setup, echo=FALSE}
library(knitr)
opts_knit$set(tidy=TRUE)
```

Flow Cytometry is a method used for detection of characteristics of cells. In this project specifically it was used to detect algal cell removal of a Picocyanobacteria (Pico) species and a Picochlorum species (Pedino). All algal cells were labelled with stable isotopes, 15N for Picocyanobacteria and 13C for Picochlorum (Pedinophyte). The flow cytometry experiment spanned from 0-180 minutes (3 hours), examining proportions of original cells removed to show efficiency of suspension feeder consumption on each panel. Several models below observe which exposed panels were experiencing higher rates of algal cell removal, Simpson's diversity index as an indicator of cell removal efficiency, and overall change in cell proportions. 

```{r}
file <- read.csv("edited_community_experiment_data.csv")
file
file <- na.omit(file)
file
```

# Organizing and subsetting data - "Pico" refers to picocyanobacteria of study and "Pedino" refers to pedinophyte of study. Time values are labelled 'Pico5, Pico10, Pedino5...' etc. in reference to minutes passed within the flow cytometry experiment for each algal species. 

```{r}
library(tidyr)
library(ggplot2)

pico_subset <- file[,c("Panel","Pico5","Pico10","Pico15","Pico20",
                       "Pico30","Pico40","Pico50","Pico60","Pico90","Pico120","Pico150","Pico180")]
head(pico_subset)

pedino_subset <- file[,c("Panel","Pedino5","Pedino10","Pedino15","Pedino20",
                       "Pedino30","Pedino40","Pedino50","Pedino60","Pedino90","Pedino120","Pedino150","Pedino180")]
head(pedino_subset)

Long_pedino = pedino_subset %>%
  pivot_longer(cols = c("Pedino5","Pedino10","Pedino15","Pedino20",
               "Pedino30","Pedino40","Pedino50","Pedino60","Pedino90","Pedino120","Pedino150","Pedino180"), names_to = c("Time"))

head(Long_pedino)

comm_pedino_data <- with(Long_pedino, tapply(value, list(Time, Panel), as.integer))
comm_pedino_data <- ifelse(is.na(comm_pedino_data), 0, comm_pedino_data)
class(comm_pedino_data)
colnames(comm_pedino_data)
comm_pedino_data
comm_pedino_data<- as.data.frame(comm_pedino_data)
comm_pedino_data


comm_pedino_data

mydf <- cbind(rownames(comm_pedino_data),comm_pedino_data)
rownames(mydf) <- NULL
colnames(mydf) <- c(names(mydf)) 
colnames(mydf)[1] <- "Time" 
class(mydf$Time)
mydf$Time <- factor(mydf$Time)
class(mydf$Time)
mydf$Time <- factor(mydf$Time, levels = c('Pedino5', 'Pedino10', 'Pedino15', 'Pedino20', 'Pedino30', 'Pedino40', 'Pedino50', 'Pedino60', 'Pedino90', 'Pedino120', 'Pedino150', 'Pedino180'))
```

## Pedinophyte Cell Removal Linear Models:

# Low diversity score - SCD_01, FC_02, IRL3_02, 
# High diversity scores- ID_03, HI_04, and FC_03
# Control- control 1, control 2, control 3


# Low diversity index panels
```{r}
ggplot(data=mydf) +
  geom_line(aes(x = Time, y=SCD_01, color= "SCD_01",group = 1))+geom_label(aes(x=12,y=50,label="0.14"), fill="white")+
  geom_line(aes(x = Time, y=FC_02, color = "FC_02", group = 1))+geom_label(aes(x=10,y=78,label="0.21"), fill="white")+
  geom_line(aes(x = Time, y=IRL3_02, color= "IRL3_02",group = 1))+geom_label(aes(x=12,y=80,label="0.3"), fill="white")+
  ylim(NA,100)+
  xlab("Time (minutes)")+
  ylab("Proportion of Original Pedinophtye cells removed (/mL)")
```

# High diversity index panels
```{r}
ggplot(data=mydf) +
  geom_line(aes(x = Time, y=ID_03, color= "ID_03",group = 1))+
  geom_line(aes(x = Time, y=HI_04, color = "HI_04", group = 1))+
  geom_line(aes(x = Time, y=FC_03, color= "FC_03",group = 1))+ 
  ylim(NA,100)+
  xlab("Time (minutes)")+
  ylab("Proportion of Original Pedinophtye cells removed (/mL)")
```

# Control Panel cell removal
```{r}
ggplot(data=mydf) +
  geom_line(aes(x = Time, y=`Control 1`, color= "Control 1",group = 1))+
  geom_line(aes(x = Time, y=`Control 2`, color = "Control 2", group = 1))+
  geom_line(aes(x = Time, y=`Control 3`, color= "Control 3",group = 1))+
  ylim(NA,100)+
  xlab("Time (minutes)")+
  ylab("Proportion of Original Pedinophtye cells removed (/mL)")
```

# High diversity (ID_03), Low diversity (SCD_01), & Control 1 Panels For Pedinophyte Cell Removal - ID_03 and SCD_01 are labelled with their calculated Simpson's Diversity Index on the representative line within the model. 
```{r}
ggplot(data=mydf) +
  geom_line(aes(x = Time, y=ID_03, color= "ID_03",group = 1))+geom_label(aes(x=12,y=100,label="0.908"), fill="white")+
  geom_line(aes(x = Time, y=SCD_01, color = "SCD_01", group = 1))+geom_label(aes(x=12,y=55,label="0.147"), fill="white")+
  geom_line(aes(x = Time, y=`Control 1`, color= "Control 1",group = 1))+ 
  ylim(NA,100)+
  xlab("Time (minutes)")+
  ylab("Proportion of Original Pedinophtye cells removed (/mL)")
```  
  
# Pivoting and subsetting Picocyanobacteria data for linear modelling
```{r}
Long_Pico = pico_subset %>% 
  pivot_longer(cols = c("Pico5","Pico10","Pico15","Pico20","Pico30","Pico40","Pico50","Pico60","Pico90","Pico120","Pico150","Pico180"), names_to = c("Time"))
head(Long_Pico)


comm_pico_data <- with(Long_Pico, tapply(value, list(Time, Panel), as.integer))
comm_pico_data <- ifelse(is.na(comm_pico_data), 0, comm_pico_data)
class(comm_pico_data)
colnames(comm_pico_data)
comm_pico_data
comm_pico_data<- as.data.frame(comm_pico_data)
comm_pico_data

mydf2 <- cbind(rownames(comm_pico_data),comm_pico_data)
rownames(mydf2) <- NULL
colnames(mydf2) <- c(names(mydf2)) 
colnames(mydf2)[1] <- "Time" 
class(mydf2$Time)
mydf2$Time <- factor(mydf2$Time)
class(mydf2$Time)
mydf2$Time <- factor(mydf2$Time, levels = c('Pico5', 'Pico10', 'Pico15', 'Pico20', 'Pico30', 'Pico40', 'Pico50', 'Pico60', 'Pico90', 'Pico120', 'Pico150', 'Pico180'))
```


## Picocyanobacteria Cell Removal Linear Models

```{r}
ggplot(data=mydf2) +
  geom_line(aes(x = Time, y=SCD_01, color= "SCD_01",group = 1))+
  geom_line(aes(x = Time, y=FC_02, color = "FC_02", group = 1))+
  geom_line(aes(x = Time, y=IRL3_02, color= "IRL3_02",group = 1))+
  ylim(NA,100)+
  xlab("Time (minutes)")+
  ylab("Proportion of Original Picocyanobacteria cells removed (/mL)")


ggplot(data=mydf2) +
  geom_line(aes(x = Time, y=ID_03, color= "ID_03",group = 1))+ geom_label(aes(x=12,y=100,label="0.9"), fill="white")+
  geom_line(aes(x = Time, y=HI_04, color = "HI_04", group = 1))+ geom_label(aes(x=11,y=89,label="0.88"),fill="white")+
  geom_line(aes(x = Time, y=FC_03, color= "FC_03",group = 1))+ geom_label(aes(x=11,y=50,label="0.76"),fill="white")+
  ylim(NA,100)+
  xlab("Time (minutes)")+
  ylab("Proportion of Original Picocyanobacteria cells removed (/mL)")


ggplot(data=mydf2) +
  geom_line(aes(x = Time, y=`Control 1`, color= "Control 1",group = 1))+
  geom_line(aes(x = Time, y=`Control 2`, color = "Control 2", group = 1))+
  geom_line(aes(x = Time, y=`Control 3`, color= "Control 3", group = 1, ))+
  ylim(NA,100)+
  xlab("Time (minutes)")+
  ylab("Proportion of Original Picocyanobacteria cells removed (/mL)")


ggplot(data=mydf2) +
  geom_line(aes(x = Time, y=ID_03, color= "ID_03",group = 1))+geom_label(aes(x=11.5,y=94,label="0.908"), fill="white")+
  geom_line(aes(x = Time, y=SCD_01, color = "SCD_01", group = 1))+geom_label(aes(x=12,y=30,label="0.147"), fill="white")+
  geom_line(aes(x = Time, y=`Control 1`, color= "Control 1",group = 1))+ 
  ylim(NA,100)+
  xlab("Time (minutes)")+
  ylab("Proportion of Original Picocyanobacteria cells removed (/mL)")


```

# The last linear regression comparisons for both species of algal cell removal show that the panels with a higher diversity index are experiencing higher efficiency of removal, and the lower diversity panels are having less efficient removal with still more than in the control panels. This data is conducive with hypotheses that an ecosystem with higher biodiversity (calculated in this study using Simpson's Diversity Index) can serve ecosystem services such as mitigation of harmful algal blooms in prone areas. Simpson's Diversity Index takes species evenness, richness, overall count, and relative abundance. 


# Overall - all panels proportion of cell removal between 150min and 180min time interval in linear ggplot as an index of each's overall ability for algal cell removal: 

```{r}
subset_plot_pedino <- subset(mydf, Time == "Pedino180" | Time == "Pedino150")
subset_plot_pedino

ggplot(data=subset_plot_pedino) +
  geom_line(aes(x = Time, y=`Control 1`, color= "Control 1",group = 1))+
  geom_line(aes(x = Time, y=`Control 2`, color ="Control 2", group = 1))+
  geom_line(aes(x = Time, y=`Control 3`, color = "Control 3", group = 1))+
  geom_line(aes(x = Time, y=FC_01, color = "FC_01", group = 1))+
  geom_line(aes(x = Time, y=FC_02, color = "FC_02", group = 1))+
  geom_line(aes(x = Time, y=FC_03, color = "FC_03", group = 1))+
  geom_line(aes(x = Time, y=HI_02, color = "HI_02", group = 1))+
  geom_line(aes(x = Time, y=HI_03, color = "HI_03", group = 1))+
  geom_line(aes(x = Time, y=HI_04, color = "HI_04", group = 1))+
  geom_line(aes(x = Time, y=ID_01, color = "ID_01", group = 1))+
  geom_line(aes(x = Time, y=ID_03, color= "ID_03", group = 1))+ 
  geom_line(aes(x = Time, y=IRL3_01, color = "IRL3_01", group = 1))+
  geom_line(aes(x = Time, y=IRL3_02, color = "IRL3_02", group = 1))+
  geom_line(aes(x = Time, y=IRL3_03, color = "IRL3_03", group = 1))+
  geom_line(aes(x = Time, y=IRL3_04, color= "IRL3_04", group = 1))+ 
  geom_line(aes(x = Time, y=MIM_01, color = "MIM_01", group = 1))+
  geom_line(aes(x = Time, y=MIM_02, color= "MIM_02", group = 1))+ 
  geom_line(aes(x = Time, y=MO_01, color= "MO_01", group = 1))+ 
  geom_line(aes(x = Time, y=MO_02, color = "MO_02", group = 1))+
  geom_line(aes(x = Time, y=MO_03, color= "MO_03", group = 1))+ 
  geom_line(aes(x = Time, y=SCD_01, color = "SCD_01", group = 1))+
  geom_line(aes(x = Time, y=SCD_02, color= "SCD_02", group = 1))+ 
  geom_line(aes(x = Time, y=SCD_03, color= "SCD_03", group = 1))+ 
  geom_line(aes(x = Time, y=SMS_01, color = "SMS_01", group = 1))+
  geom_line(aes(x = Time, y=SMS_03, color = "SMS_03", group = 1))+
  geom_line(aes(x = Time, y=WP_01, color= "WP_01", group = 1))+ 
  geom_line(aes(x = Time, y=WP_03, color = "WP_03", group = 1))+
  geom_line(aes(x = Time, y=WP_04, color= "WP_04", group = 1))+ 
  ylim(NA,100)+
  xlab("Time (minutes)")+
  ylab("Proportion of Original Pedinophtye cells removed (/mL)") + 
  ggtitle("Pedinophyte Cell Removal Across all Panels (150-180min")
```


##Above is pedinophyte overall panel cell removal, below is picocyanobacteria. 

```{r}
subset_plot_pico <- subset(mydf2, Time == "Pico180" | Time == "Pico150")
subset_plot_pico

ggplot(data=subset_plot_pico) +
  geom_line(aes(x = Time, y=`Control 1`, color= "Control 1",group = 1))+
  geom_line(aes(x = Time, y=`Control 2`, color ="Control 2", group = 1))+
  geom_line(aes(x = Time, y=`Control 3`, color = "Control 3", group = 1))+
  geom_line(aes(x = Time, y=FC_01, color = "FC_01", group = 1))+
  geom_line(aes(x = Time, y=FC_02, color = "FC_02", group = 1))+
  geom_line(aes(x = Time, y=FC_03, color = "FC_03", group = 1))+
  geom_line(aes(x = Time, y=HI_02, color = "HI_02", group = 1))+
  geom_line(aes(x = Time, y=HI_03, color = "HI_03", group = 1))+
  geom_line(aes(x = Time, y=HI_04, color = "HI_04", group = 1))+
  geom_line(aes(x = Time, y=ID_01, color = "ID_01", group = 1))+
  geom_line(aes(x = Time, y=ID_03, color= "ID_03", group = 1))+ 
  geom_line(aes(x = Time, y=IRL3_01, color = "IRL3_01", group = 1))+
  geom_line(aes(x = Time, y=IRL3_02, color = "IRL3_02", group = 1))+
  geom_line(aes(x = Time, y=IRL3_03, color = "IRL3_03", group = 1))+
  geom_line(aes(x = Time, y=IRL3_04, color= "IRL3_04", group = 1))+ 
  geom_line(aes(x = Time, y=MIM_01, color = "MIM_01", group = 1))+
  geom_line(aes(x = Time, y=MIM_02, color= "MIM_02", group = 1))+ 
  geom_line(aes(x = Time, y=MO_01, color= "MO_01", group = 1))+ 
  geom_line(aes(x = Time, y=MO_02, color = "MO_02", group = 1))+
  geom_line(aes(x = Time, y=MO_03, color= "MO_03", group = 1))+ 
  geom_line(aes(x = Time, y=SCD_01, color = "SCD_01", group = 1))+
  geom_line(aes(x = Time, y=SCD_02, color= "SCD_02", group = 1))+ 
  geom_line(aes(x = Time, y=SCD_03, color= "SCD_03", group = 1))+ 
  geom_line(aes(x = Time, y=SMS_01, color = "SMS_01", group = 1))+
  geom_line(aes(x = Time, y=SMS_03, color = "SMS_03", group = 1))+
  geom_line(aes(x = Time, y=WP_01, color= "WP_01", group = 1))+ 
  geom_line(aes(x = Time, y=WP_03, color = "WP_03", group = 1))+
  geom_line(aes(x = Time, y=WP_04, color= "WP_04", group = 1))+ 
  ylim(NA,100)+
  xlab("Time (minutes)")+
  ylab("Proportion of Original Picocyanobacteria cells removed (/mL)") +
  ggtitle("Picocyanobacteria Cell Removal Across all Panels (150-180min")
```






