---
title: "IRL_Isotope"
author: "Lexie DelViscio"
date: "4/4/2022"
output: html_document
---

```{r setup, echo=FALSE}
library(knitr)
opts_knit$set(tidy=TRUE)
```

## R Markdown
Lets start by loading in libraries we will need 
Download instructions for PriceTools is in the scripts folder if not already installed
```{r}
library("xlsx")
library(ggplot2)
library(forcats)
library(tidyr)
library(dplyr)
library(priceTools)
library(vegan)
library(dummies)
library(gridExtra)
```

and the data we will be using. 
```{r}
isotope_data <- read.xlsx("edited_community_isotope_data.xlsx",2)
```

Simple visualization of the data
```{r}
head(isotope_data)
unique(isotope_data$Taxa)
```
The values contained in the columns pedino_13C_enrichment and pico_15N_enrichment represent proxies for efficient removal and assimilation of nutrients from enriched Picochlorum sp (referred to as pedino throughout) and Picocyanobacteria (referred to as pico throughout)

The values contained in the columns atom_13C_percent and atom_15N_percent represent another way to express "enrichment" in 13C that would be caused by consuming algae that have been labeled with 13C and in 15N that would be caused by consuming algae that have been labeled with 15N.

Barplots of the Means across each column of interest for Taxa
```{r}
#barplots by taxa means
par(mfrow=c(2,2))
color_vector_taxa = rev(rainbow(length(unique(isotope_data$Taxa))))
mean_taxa_pedino = tapply(isotope_data$pedino_13C_enrichment, isotope_data$Taxa, mean)
mean_taxa_pedino_percent = tapply(isotope_data$atom_13C_percent,isotope_data$Taxa, mean)
barplot(mean_taxa_pedino,las=2, col = color_vector_taxa, ylab = 'Pedino Enrichment (13C) Mean', main = "Pedino Enrichment Mean vs. Taxa")
barplot(mean_taxa_pedino_percent, las=2, ylim=c(0.0, 1.2), col = color_vector_taxa, ylab = 'Pedino 13C atom% mean', main = "Pedino Atom% vs. Taxa")

mean_taxa_pico = tapply(isotope_data$pico_15N_enrichment, isotope_data$Taxa, mean)
mean_taxa_pico_percent = tapply(isotope_data$atom_15N_percent,isotope_data$Taxa, mean)
barplot(mean_taxa_pico,las=2, col = color_vector_taxa, ylab = "Pico Enrichment (15N) Mean", main = "Pico Enrichment Mean vs. Taxa")
barplot(mean_taxa_pico_percent, las=2, col = color_vector_taxa,ylab = "Pico Atom% (15N)", main = "Pico Atom% Mean vs. Taxa")
```

Barplots of the Means across variable each column for Site
```{r}
#barplots by site
par(mfrow=c(2,2))
color_vector_site = rev(terrain.colors(length(unique(isotope_data$Taxa))))
mean_site_pedino = tapply(isotope_data$pedino_13C_enrichment, isotope_data$Panel_Site, mean)
mean_site_pedino_percent = tapply(isotope_data$atom_13C_percent,isotope_data$Panel_Site, mean)
barplot(mean_site_pedino,las=2, col = color_vector_site, ylab = "Pedino Enrichment (13C) Mean", main = "Pedino Enrichment vs Site")
barplot(mean_site_pedino_percent, las=2, ylim=c(0.0, 1.2), col = color_vector_site,ylab = "Pedino Atom% (13C)", main = "Pedino Atom% Mean vs. Site")

mean_site_pico = tapply(isotope_data$pico_15N_enrichment, isotope_data$Panel_Site, mean)
mean_site_pico_percent = tapply(isotope_data$atom_15N_percent,isotope_data$Panel_Site, mean)
barplot(mean_site_pico,las=2, col = color_vector_site, ylab = "Pico Enrichment (15N) Mean", main = "Pico Enrichment Mean vs. Site")
barplot(mean_site_pico_percent, las=2, col = color_vector_site,ylab = "Pico Atom% (15N) Mean", main = "Pico Atom% Mean vs. Site")
```
Now we will make some boxplots for Taxa and Enrichment
```{r}
boxplot1 <- ggplot(data = isotope_data) + 
  geom_boxplot(mapping = aes(x = Taxa, y = pedino_13C_enrichment, color = Taxa)) +  
  labs(x = 'Taxa', y = 'pedino_13C_enrichment', title = 'taxa vs pedino_13C_enrichment') + theme(axis.text.x = element_text(angle = 90))

boxplot2 <- ggplot(data = isotope_data) + 
  geom_boxplot(mapping = aes(x = Taxa, y = pico_15N_enrichment, color = Taxa)) +  labs(x = 'Taxa', y = 'pico_15N_enrichment', title = 'taxa vs pico_15N_enrichment') + theme(axis.text.x = element_text(angle = 90))

grid.arrange(boxplot1, boxplot2, nrow = 1)
```

As well as boxplots for Taxa and Atom %
```{r}
#Pedino
boxplot3 <- ggplot(data = isotope_data) + 
  geom_boxplot(mapping = aes(x = Taxa, y = atom_13C_percent, color = Taxa)) +  
  labs(x = 'Taxa', y = 'atom 13C %', title = 'taxa vs pedino 13C %') + theme(axis.text.x = element_text(angle = 90))

#pico
boxplot4 <- ggplot(data = isotope_data) + 
  geom_boxplot(mapping = aes(x = Taxa, y = atom_15N_percent, color = Taxa)) +  
  labs(x = 'Taxa', y = "atom 15N %", title = 'taxa vs pico 15N %') + theme(axis.text.x = element_text(angle = 90))
 
grid.arrange(boxplot3,boxplot4, nrow = 1)
```

basic taxa linear regression pedino
```{r}
pedino_taxa_lm = lm(isotope_data$pedino_13C_enrichment ~ -1 + isotope_data$Taxa)
summary(pedino_taxa_lm)
```

basic taxa linear regression pico
```{r}
pico_taxa_lm = lm(isotope_data$pico_15N_enrichment ~ -1 + isotope_data$Taxa)
summary(pico_taxa_lm)
```

Now we will create a dummy matrix (isotope_copy) in order to reorder the factor levels of Species ID by Taxa to graph a master plot of the Species and Enrichment values in an organized manner

```{r}
isotope_copy <- isotope_data
isotope_copy$Species_ID <- factor(isotope_copy$Species_ID)
isotope_copy$Species_ID <- fct_reorder(isotope_copy$Species_ID, isotope_copy$Taxa, .fun = max)
```

Species versus Pedino Enrichment
```{r}
ggplot(data = isotope_copy) + 
  geom_boxplot(mapping = aes(x = Species_ID, y = pedino_13C_enrichment, color=Taxa)) +  
  labs(x = 'species_id', y = 'pedino_13C_enrichment', title = 'species vs pedino_13C_enrichment master') + theme(axis.text.x = element_text(angle = 90))
```

Species versus Pico enrichment
```{r}
ggplot(data = isotope_copy) +
  geom_boxplot(mapping = aes(x = Species_ID, y = pico_15N_enrichment, color=Taxa)) +  
  labs(x = 'species_id', y = 'pico_15N_enrichment', title = 'species vs pico_15N_enrichment master') + theme(axis.text.x = element_text(angle = 90))
```

Boxplots for enrichment by taxa mean- per panel


FC
```{r}
FC_isotope <- subset(isotope_copy, isotope_copy$Panel_Site == "FC")
FC_bp1 <- ggplot(data = FC_isotope) + 
  geom_boxplot(mapping = aes(x = Species_ID, y = pedino_13C_enrichment, color=Taxa)) +  
  labs(x = 'species_id', y = 'pedino_13C_enrichment', title = 'species vs pedino_13C_enrichment FC') + theme(axis.text.x = element_text(angle = 90))

FC_bp2 <- ggplot(data = FC_isotope) + 
  geom_boxplot(mapping = aes(x = Species_ID, y = pico_15N_enrichment, color=Taxa)) +  
  labs(x = 'species_id', y = 'pico_15N_enrichment', title = 'species vs pico_15N_enrichment FC') + theme(axis.text.x = element_text(angle = 90))

grid.arrange(FC_bp1,FC_bp2, nrow = 1)

```

HI
```{r}
HI_isotope <- subset(isotope_copy, isotope_copy$Panel_Site == "HI")
HI_bp1 <- ggplot(data = HI_isotope) + 
  geom_boxplot(mapping = aes(x = Species_ID, y = pedino_13C_enrichment, color=Taxa)) +  
  labs(x = 'species_id', y = 'pedino_13C_enrichment', title = 'species vs pedino_13C_enrichment HI') + theme(axis.text.x = element_text(angle = 90))

HI_bp2 <- ggplot(data = HI_isotope) + 
  geom_boxplot(mapping = aes(x = Species_ID, y = pico_15N_enrichment, color=Taxa)) +  
  labs(x = 'species_id', y = 'pico_15N_enrichment', title = 'species vs pico_15N_enrichment HI') + theme(axis.text.x = element_text(angle = 90))

grid.arrange(HI_bp1,HI_bp2, nrow = 1)

```

ID
```{r}
ID_isotope <- subset(isotope_copy, isotope_copy$Panel_Site == "ID")
ID_bp1 <- ggplot(data = ID_isotope) + 
  geom_boxplot(mapping = aes(x = Species_ID, y = pedino_13C_enrichment, color=Taxa)) +  
  labs(x = 'species_id', y = 'pedino_13C_enrichment', title = 'species vs pedino_13C_enrichment ID') + theme(axis.text.x = element_text(angle = 90))

ID_bp2 <- ggplot(data = ID_isotope) + 
  geom_boxplot(mapping = aes(x = Species_ID, y = pico_15N_enrichment, color=Taxa)) +  
  labs(x = 'species_id', y = 'pico_15N_enrichment', title = 'species vs pico_15N_enrichment ID') + theme(axis.text.x = element_text(angle = 90))

grid.arrange(ID_bp1,ID_bp2, nrow = 1)
```

IRL_3
```{r}
IRL3_isotope <- subset(isotope_copy, isotope_copy$Panel_Site == "IRL3")
IRL3_bp1 <- ggplot(data = IRL3_isotope) + 
  geom_boxplot(mapping = aes(x = Species_ID, y = pedino_13C_enrichment, color=Taxa)) +  
  labs(x = 'species_id', y = 'pedino_13C_enrichment', title = 'species vs pedino_13C_enrichment IRL3') + theme(axis.text.x = element_text(angle = 90))

IRL3_bp2 <- ggplot(data = IRL3_isotope) + 
  geom_boxplot(mapping = aes(x = Species_ID, y = pico_15N_enrichment, color=Taxa)) +  
  labs(x = 'species_id', y = 'pico_15N_enrichment', title = 'species vs pico_15N_enrichment IRL3') + theme(axis.text.x = element_text(angle = 90))

grid.arrange(IRL3_bp1,IRL3_bp2, nrow = 1)

```

MIM
```{r}
MIM_isotope <- subset(isotope_copy, isotope_copy$Panel_Site == "MIM")
MIM_bp1 <- ggplot(data = MIM_isotope) + 
  geom_boxplot(mapping = aes(x = Species_ID, y = pedino_13C_enrichment, color=Taxa)) +  
  labs(x = 'species_id', y = 'pedino_13C_enrichment', title = 'species vs pedino_13C_enrichment MIM') + theme(axis.text.x = element_text(angle = 90))

MIM_bp2 <- ggplot(data = MIM_isotope) + 
  geom_boxplot(mapping = aes(x = Species_ID, y = pico_15N_enrichment, color=Taxa)) +  
  labs(x = 'species_id', y = 'pico_15N_enrichment', title = 'species vs pico_15N_enrichment MIM') + theme(axis.text.x = element_text(angle = 90))

grid.arrange(MIM_bp1,MIM_bp2, nrow = 1)

```

MO2
```{r}
MO2_isotope <- subset(isotope_copy, isotope_copy$Panel_Site == "MO2")
MO2_bp1 <- ggplot(data = MO2_isotope) + 
  geom_boxplot(mapping = aes(x = Species_ID, y = pedino_13C_enrichment, color=Taxa)) +  
  labs(x = 'species_id', y = 'pedino_13C_enrichment', title = 'species vs pedino_13C_enrichment MO2') + theme(axis.text.x = element_text(angle = 90))

MO2_bp2 <- ggplot(data = MO2_isotope) + 
  geom_boxplot(mapping = aes(x = Species_ID, y = pico_15N_enrichment, color=Taxa)) +  
  labs(x = 'species_id', y = 'pico_15N_enrichment', title = 'species vs pico_15N_enrichment MO2') + theme(axis.text.x = element_text(angle = 90))

grid.arrange(MO2_bp1,MO2_bp2, nrow = 1)

```

SCD
```{r}
SCD_isotope <- subset(isotope_copy, isotope_copy$Panel_Site == "SCD")
SCD_bp1 <- ggplot(data = SCD_isotope) + 
  geom_boxplot(mapping = aes(x = Species_ID, y = pedino_13C_enrichment, color=Taxa)) +  
  labs(x = 'species_id', y = 'pedino_13C_enrichment', title = 'species vs pedino_13C_enrichment SCD') + theme(axis.text.x = element_text(angle = 90))

SCD_bp2 <- ggplot(data = SCD_isotope) + 
  geom_boxplot(mapping = aes(x = Species_ID, y = pico_15N_enrichment, color=Taxa)) +  
  labs(x = 'species_id', y = 'pico_15N_enrichment', title = 'species vs pico_15N_enrichment SCD') + theme(axis.text.x = element_text(angle = 90))

grid.arrange(SCD_bp1,SCD_bp2, nrow = 1)

```

SMS
```{r}
SMS_isotope <- subset(isotope_copy, isotope_copy$Panel_Site == "SMS")
SMS_bp1 <- ggplot(data = SMS_isotope) + 
  geom_boxplot(mapping = aes(x = Species_ID, y = pedino_13C_enrichment, color=Taxa)) +  
  labs(x = 'species_id', y = 'pedino_13C_enrichment', title = 'species vs pedino_13C_enrichment SMS') + theme(axis.text.x = element_text(angle = 90))

SMS_bp2 <- ggplot(data = SMS_isotope) + 
  geom_boxplot(mapping = aes(x = Species_ID, y = pico_15N_enrichment, color=Taxa)) +  
  labs(x = 'species_id', y = 'pico_15N_enrichment', title = 'species vs pico_15N_enrichment SMS') + theme(axis.text.x = element_text(angle = 90))

grid.arrange(SMS_bp1,SMS_bp2, nrow = 1)

```

WP
```{r}
WP_isotope <- subset(isotope_copy, isotope_copy$Panel_Site == "WP")
WP_bp1 <- ggplot(data = WP_isotope) + 
  geom_boxplot(mapping = aes(x = Species_ID, y = pedino_13C_enrichment, color=Taxa)) +  
  labs(x = 'species_id', y = 'pedino_13C_enrichment', title = 'species vs pedino_13C_enrichment WP') + theme(axis.text.x = element_text(angle = 90))

WP_bp2 <- ggplot(data = WP_isotope) + 
  geom_boxplot(mapping = aes(x = Species_ID, y = pico_15N_enrichment, color=Taxa)) +  
  labs(x = 'species_id', y = 'pico_15N_enrichment', title = 'species vs pico_15N_enrichment WP') + theme(axis.text.x = element_text(angle = 90))

grid.arrange(WP_bp1,WP_bp2, nrow = 1)
```

subsetting the species of algae
```{r}
pedino_subset <- isotope_data[c('Site_and_Panel',"Species_ID","pedino_13C_enrichment","atom_13C_percent")]
pico_subset <- isotope_data[c('Site_and_Panel',"Species_ID","pico_15N_enrichment", "atom_15N_percent")]
```

creating community matrixes
```{r}
comm_pedino <- with(pedino_subset, tapply(pedino_13C_enrichment, list(Site_and_Panel, Species_ID), sum))
comm_pedino <- ifelse(is.na(comm_pedino), 0, comm_pedino)


comm_pico <- with(pico_subset, tapply(pico_15N_enrichment, list(Site_and_Panel, Species_ID), sum))
comm_pico <- ifelse(is.na(comm_pico), 0, comm_pico)
head(comm_pico)

```

pico pca
```{r}
pico_pca = rda(comm_pico, scale = TRUE)
pico_pca
```

```{r}
# the eigenvalues sum up to equal the total interia (i.e., total variance in this case)
sum(pico_pca$CA$eig)
```

```{r}
# the ratio of the eigenvalue to the total variance is the amount of 
# variance explained by each PCA axis
round(pico_pca$CA$eig / pico_pca$tot.chi, 2)
#We can see from above that the PCA axis 1 captures approximately 17% of the total variance in the community matrix. Let's graph the data to better get a sense of the correlation structure.
```

```{r}
biplot(pico_pca)
```

```{r}
ordiplot(pico_pca, display = 'species', type = "text")
ordiplot(pico_pca,display="sites", type = "text")
fig <- ordiplot(pico_pca)
text(fig,"species",col="red",cex=.8)
points(fig,"sites",col="blue",cex=0.8)
```
ID_03, HI_04, ID_01, and FC_03 all seem to have strong correlations with either PC1 or PC2, and so are worth investigating closely in an individual panel analysis.  

pedino pca
```{r}
pedino_pca = rda(comm_pedino, scale = TRUE)
pedino_pca
```

```{r}
par(mfrow= c(1,1))
# the eigenvalues sum up to equal the total interia (i.e., total variance in this case)
sum(pedino_pca$CA$eig)
```

```{r}
# the ratio of the eigenvalue to the total variance is the amount of 
# variance explained by each PCA axis

round(pedino_pca$CA$eig / pedino_pca$tot.chi, 2)

#We can see from above that the PCA axis 1 captures approximately 16% of the total variance in the community matrix. Let's graph the data to better get a sense of the correlation structure.
```

```{r}
biplot(pedino_pca)
```

```{r}
ordiplot(pedino_pca, display = 'species',type="text")
ordiplot(pedino_pca,display = 'sites',type="text")
fig <- ordiplot(pedino_pca)
text(fig,"species",col="red",cex=0.8)
points(fig,"sites",col="blue",cex=0.8)
```
I still want to do more work with these community matrixes, specifically relating to the species that are doing the most removal, and when.


ID_03, HI_04, ID_01, and FC_03 
```{r}
ID_03_subset <- subset(isotope_copy, isotope_copy$Site_and_Panel == "ID_03")
head(ID_03_subset)

ID_03_bp1 <- ggplot(data = ID_03_subset) + 
  geom_boxplot(mapping = aes(x = Species_ID, y = pedino_13C_enrichment, color=Taxa)) +  
  labs(x = 'species_id', y = 'pedino_13C_enrichment', title = 'species vs pedino_13C_enrichment WP') + theme(axis.text.x = element_text(angle = 90))

ID_03_bp2 <- ggplot(data = ID_03_subset) + 
  geom_boxplot(mapping = aes(x = Species_ID, y = pico_15N_enrichment, color=Taxa)) +  
  labs(x = 'species_id', y = 'pico_15N_enrichment', title = 'species vs pico_15N_enrichment WP') + theme(axis.text.x = element_text(angle = 90))

grid.arrange(ID_03_bp1,ID_03_bp2, nrow = 1)

```
```{r}
HI_04_subset <- subset(isotope_copy, isotope_copy$Site_and_Panel == "HI_04")
head(HI_04_subset)

HI_04_bp1 <- ggplot(data = HI_04_subset) + 
  geom_boxplot(mapping = aes(x = Species_ID, y = pedino_13C_enrichment, color=Taxa)) +  
  labs(x = 'species_id', y = 'pedino_13C_enrichment', title = 'species vs pedino_13C_enrichment WP') + theme(axis.text.x = element_text(angle = 90))

HI_04_bp2 <- ggplot(data = HI_04_subset) + 
  geom_boxplot(mapping = aes(x = Species_ID, y = pico_15N_enrichment, color=Taxa)) +  
  labs(x = 'species_id', y = 'pico_15N_enrichment', title = 'species vs pico_15N_enrichment WP') + theme(axis.text.x = element_text(angle = 90))

grid.arrange(HI_04_bp1,HI_04_bp2, nrow = 1)
```


```{r}
ID_01_subset <- subset(isotope_copy, isotope_copy$Site_and_Panel == "ID_01")
head(ID_01_subset)
ID_01_bp1 <- ggplot(data = ID_01_subset) + 
  geom_boxplot(mapping = aes(x = Species_ID, y = pedino_13C_enrichment, color=Taxa)) +  
  labs(x = 'species_id', y = 'pedino_13C_enrichment', title = 'species vs pedino_13C_enrichment WP') + theme(axis.text.x = element_text(angle = 90))

ID_01_bp2 <- ggplot(data = ID_01_subset) + 
  geom_boxplot(mapping = aes(x = Species_ID, y = pico_15N_enrichment, color=Taxa)) +  
  labs(x = 'species_id', y = 'pico_15N_enrichment', title = 'species vs pico_15N_enrichment WP') + theme(axis.text.x = element_text(angle = 90))

grid.arrange(ID_01_bp1,ID_01_bp2, nrow = 1)

```


```{r}
FC_03_subset <- subset(isotope_copy, isotope_copy$Site_and_Panel == "FC_03")
head(FC_03_subset)
FC_03_bp1 <- ggplot(data = FC_03_subset) + 
  geom_boxplot(mapping = aes(x = Species_ID, y = pedino_13C_enrichment, color=Taxa)) +  
  labs(x = 'species_id', y = 'pedino_13C_enrichment', title = 'species vs pedino_13C_enrichment WP') + theme(axis.text.x = element_text(angle = 90))

FC_03_bp2 <- ggplot(data = FC_03_subset) + 
  geom_boxplot(mapping = aes(x = Species_ID, y = pico_15N_enrichment, color=Taxa)) +  
  labs(x = 'species_id', y = 'pico_15N_enrichment', title = 'species vs pico_15N_enrichment WP') + theme(axis.text.x = element_text(angle = 90))

grid.arrange(FC_03_bp1,FC_03_bp2, nrow = 1)


```

as compared to a site which was in the centeroid rather than associated along an axis in the pca SMS_02.

```{r}
SCD_01_subset <- subset(isotope_copy, isotope_copy$Site_and_Panel == "SCD_01")


SCD_01_bp1 <- ggplot(data = SCD_01_subset) + 
  geom_boxplot(mapping = aes(x = Species_ID, y = pedino_13C_enrichment, color=Taxa)) +  
  labs(x = 'species_id', y = 'pedino_13C_enrichment', title = 'species vs pedino_13C_enrichment WP') + theme(axis.text.x = element_text(angle = 90))

SCD_01_bp2 <- ggplot(data = SCD_01_subset) + 
  geom_boxplot(mapping = aes(x = Species_ID, y = pico_15N_enrichment, color=Taxa)) +  
  labs(x = 'species_id', y = 'pico_15N_enrichment', title = 'species vs pico_15N_enrichment WP') + theme(axis.text.x = element_text(angle = 90))

grid.arrange(SCD_01_bp1, SCD_01_bp2, nrow = 1)

```
We can see that the four sites highly associated with the axis of variance are each composed of a variance of taxa, as well as indicator species amongst each that seem to be doing the most removal (becomming the most enriched). The key point here however is that these all are more diverse within their structure as can be seen in the different taxa presented, and they are more connected to the axis of variation in the pca analysis than the panel SMS_02 which is not associated with pca axis 1 or 2 more strongly and only has one species showing no diversity. 

The above point is further proven by the simpsons evenness index values for each of the specified panels. 

The strongly correlated sites all have a high simpsons diversity index
ID_03
.91
HI_04
.88
ID_01
.88
FC_03
.77

The site with low correlation to the pca axis has a low simpsons diversity index
SCD_01
.15

This shows that diversity does play an affect on isotope removal.


Simpsons Diversity Index as calculated in Lexie_Distribution.Rmd
    FC_01     FC_02     FC_03     FC_04     HI_01     HI_02     HI_03     HI_04     ID_01     ID_03   IRL3_01 
0.7635243 0.2150518 0.7671967 0.2302145 0.4416106 0.7507244 0.5786848 0.8808834 0.8816872 0.9085950 0.7160000 
  IRL3_02   IRL3_03   IRL3_04    MIM_01    MIM_02     MO_01     MO_02     MO_03    SCD_01    SCD_02    SCD_03 
0.3076633 0.7300296 0.6043925 0.4428711 0.4349174 0.7611791 0.7485370 0.7399773 0.1477990 0.1817325 0.1973003 
   SMS_01    SMS_03     WP_01     WP_03     WP_04 
0.7237451 0.5920168 0.5646149 0.5330642 0.3648000 

Investigating individual species showing strong(er) axis correlation


```{r}

species_1 <- subset(isotope_copy,subset = Species_ID == 'Halichondria cf magniconulosa')
species_1


```
although only found on one panel, this species lined up most closely with the same axis as the panel it was found on. It also seems to be doing the most amount of removal in the panel. Since there is only one instance it of this species, and it is a panel with a high diversity 




