---
title: "IRL_Lexie_Distribution"
author: "Lexie DelViscio"
date: "4/5/2022"
output: html_document
---

```{r setup, echo=False}
library(knitr)
opts_knit$set(tidy=TRUE)
```
This is all extremely preliminary visualizations for panels and data organization

loading libraries
```{r}
library("xlsx")
library(vegan)
library(dummies)
library(tidyr)

```


```{r}
community_panel_data <- read.xlsx("edited_community_experiment_data.xlsx",3)
community_panel_data = subset(community_panel_data, select = -c(NA.))
head(community_panel_data)
```


```{r}
plot(community_panel_data$FC_01[which(community_panel_data$FC_01 > 0)])
text(community_panel_data$FC_01[which(community_panel_data$FC_01 > 0)], labels=community_panel_data$Species[which(community_panel_data$FC_01 > 0)], cex=0.9, font=1)
```

```{r}
plot(community_panel_data$FC_02[which(community_panel_data$FC_02 > 0)])
text(community_panel_data$FC_02[which(community_panel_data$FC_02 > 0)], labels=community_panel_data$Species[which(community_panel_data$FC_02 > 0)], cex=0.9, font=1)
```

```{r}
plot(community_panel_data$FC_03[which(community_panel_data$FC_03 > 0)])
text(community_panel_data$FC_03[which(community_panel_data$FC_03 > 0)], labels=community_panel_data$Species[which(community_panel_data$FC_03 > 0)], cex=0.9, font=1)
```

```{r}
plot(community_panel_data$FC_04[which(community_panel_data$FC_04 > 0)])
text(community_panel_data$FC_04[which(community_panel_data$FC_04 > 0)], labels=community_panel_data$Species[which(community_panel_data$FC_04 > 0)], cex=0.9, font=1)
```

pivot the data longer
```{r}
Long_community_panel = community_panel_data %>%
  pivot_longer(cols = c(FC_01, FC_02, FC_03, FC_04, HI_01, HI_02, HI_03, HI_04,ID_01, ID_03, IRL3_01, IRL3_02, IRL3_03, IRL3_04, MIM_01, MIM_02, MO_01, MO_02, MO_03, SCD_01,SCD_02, SCD_03, SMS_01, SMS_03, WP_01, WP_03, WP_04), names_to = c("Site"))
Long_community_panel$value <- as.integer(as.character(Long_community_panel$value)) 
head(Long_community_panel)
```


I will also investigate s.PIE, Or Simpsons evenness index as well as, the abundance by sites for each panel in order to get a measurement of evenness. The measure of evenness can be plotted against the traits frannies is deriving from flow cytometry in the end. 


```{r}
comm_data <- with(Long_community_panel, tapply(value, list(Site, Species), as.integer))
comm_data <- ifelse(is.na(comm_data), 0, comm_data)
```

```{r}
diversity_indexes <- diversity(comm_data,"simpson")
diversity_indexes
sort(diversity_indexes)
```

